---
title: "Programming Exercises"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# show code in output
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Exercise 1

Turn the following code into a function named `qq_norm` taking the sample data 
as an argument and returning the slope and intercept in a list.

```{r qq_norm}
## work out slope and intercept of line for quantile-quantile plot
q_sample <- quantile(y, # sample data
                     c(0.25, 0.75), # quantiles to compute (only need 2)
                     names = FALSE, na.rm = TRUE)
q_theory <- qnorm(c(0.25, 0.75)) # work out theoretical quantiles
slope <- diff(q_sample) / diff(q_theory) # slope = (y2 - y1)/(x2 - x1)
intercept <- q_sample[1] - slope * q_theory[1] # intercept = y1 - slope*x1
```

Run the `qq_norm` chunk to source your new function, then run the 
`normal-QQ` chunk below, which uses the `qq_norm` function to compute 
parameters for an example plot.

```{r normal-QQ}
# simulate random sample from a normal distribution
y <- rnorm(1000, 100, 5)

# find parameters of line to add to QQ-plot
par <- qq_norm(y)

# QQ-plot (vs standard normal, should fall along line)
dat <- data.frame(sample = y, theoretical = rnorm(1000))
ggplot(dat, aes(x = sort(theoretical), y = sort(sample))) +
    geom_point() +
    geom_abline(slope = par$slope,
                intercept = par$intercept)
```

## Exercise 2

Copy your `qq_norm()` fuction to the `qq` chunk below and rename the function `qq`. 

Add a new argument `fun` to specify any quantile function (e.g. `qt`, `qf`, 
etc). Give it the default value `qnorm`. 

Inside the function use `qfun <- match.fun(fun)` to get 
the quantile function matching `fun`, then use `qfun` instead of `qnorm` 
to compute `q_theory`. Use `...` to pass on arguments to `qfun`.

```{r qq}
## work out slope and intercept of line for Q-Q plot any theoretical distribution

```

Run the `qq` chunk and test your function on the `t-QQ` chunk below.

```{r t-QQ}
# compute two sample t statistics for 1000 simulated normal samples of size 10
t_statistic <- function(n) {
    x <- rnorm(n)
    y <- rnorm(n)
    t.test(x, y)$statistic
}
tstat <- replicate(1000, t_statistic(10))

# find parameters of line to add to QQ-plot
# based on simulated t-statistics and reference t_18 distribution
par <- qq(tstat, qt, df = 18)

## QQ-plot
dat <- data.frame(sample = tstat, theoretical = tval)
ggplot(dat, aes(x = sort(theoretical), y = sort(sample))) +
    geom_point() +
    geom_abline(slope = par$slope,
                intercept = par$intercept)

```


